What we {\sf eval} in the shadows

### 2021-04-01 paper/main.tex
Environments

\author{Author }
\authornote{Both authors contributed equally to this research.}
\email{a@b.com}
\orcid{}
\author{Author}
\authornotemark[1]
\email{r@s.com}
\affiliation{\institution{Institute}}

@@

%%%%%%%% JAN:::: NOT SURE WHAT THIS IS
%% It refers to the \emph{namespace} of a package. A call to
%% \c{library(packageName)}, which load libraries in R, for instance, will populate
%% environment \c{package:packageName}. It is a \emph{base} function though, so we
%% do not see it in the CRAN dataset. However, R still makes it possible to access
%% any package environments and \packageNbPackageEnvSites call sites, \ie
%% \packagePackageEnvSitePercent access a package environment, from
%% \packageNbPackageEnvPackages different packages. Those packages perform
%% introspection, to represent and search any environment by name, in package
%% \emph{envnames}, to containerize tests, as with \emph{testthat} and
%% \emph{unitizer}, to create a custom OOP system with \emph{R.oo}, or to create
%% poor man's hidden functions in \emph{USSCXenaTools}.

%% It is also used to implement a custom caching mechanism in packages
%% \emph{g.data} and \emph{SOAR}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\subsubsection{The expression passed to \eval.}
\paragraph{Touching package environments.}

\paragraph{Base}
The ranking of minimized expressions in \emph{base} is similar to the one in
CRAN bu the share of \c{V} is much larger, as it is present in
\baseMinimizedpropsitesa\% of the sites and \c{X} is a distant second, in
\baseMinimizedpropsitesb\% of the sites.

>>>>

\author{Author }
\authornote{Both authors contributed equally to this research.}
\email{a@b.com}
\orcid{}
\author{Author}
\authornotemark[1]
\email{r@s.com}
\affiliation{\institution{Institute} \country{Country}}

@@

%%%%%%%% JAN:::: NOT SURE WHAT THIS IS
% The namespace stuff of packages was meant for the description of the envir argument.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\paragraph{Base}
The ranking of minimized expressions in \emph{base} is similar to the one in
CRAN but the share of \c{V} is much larger, as it is present in
\baseMinimizedpropsitesa\% of the sites and \c{X} is a distant second, in
\baseMinimizedpropsitesb\% of the sites.

@@

\paragraph{Package environments.} Another kind of environments that is passed to \eval is the environment of a package. 
 It refers to the \emph{namespace} of a package. A call to
 \c{library(packageName)}, which load libraries in R, for instance, will populate
 environment \c{package:packageName}. It is a \emph{base} function though, so we
 do not see it in the CRAN dataset. However, R still makes it possible to access
 any package environments and \packageNbPackageEnvSites call sites, \ie
 \packagePackageEnvSitePercent access a package environment, from
 \packageNbPackageEnvPackages different packages. Those packages perform
 introspection, to represent and search any environment by name, in package
 \emph{envnames}, to containerize tests, as with \emph{testthat} and
 \emph{unitizer}, to create a custom OOP system with \emph{R.oo}, or to create
 poor man's hidden functions in \emph{USSCXenaTools}.

 It is also used to implement a custom caching mechanism in packages
 \emph{g.data} and \emph{SOAR}.
